Next Trippy Structures\thanks{Supported by organization x.}

### 2019-03-14 paper.tex
Nieves-ready

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
With an increasing adoption of passenger tracking technology on public transportation networks, it is becoming necessary to store a constantly growing amount of information regarding the usage (demand) of the networks, which is different from the well-known information of stops and timetables (offer). To enable analysis over these large collections of data, a compact yet indexed representation is needed that, unlike the works that focus on indexing moving objects, allows for representation and querying of relevant network elements related to passenger trips.

@@

Because smart card methods usually provide only information about boarding stops, there are works that study the challenge of inferring alighting stops from passengers \ref{wang2011review}. In addition, the authors of \cite{tao2014exploring} have specifically tackled the challenge of reconstructing full trajectories, accounting for trip-chaining, by using data obtained from smart cards. Furthermore, in \cite{alsger2016validating} it is also proven that not only the alighting stops, but also the (last) destination stop of a trip can be estimated from boarding data gathered by a smart card, within a reasonable accuracy.

>>>>

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
With the increasing use of passenger tracking technology on public transportation networks, it is becoming necessary to store a constantly growing amount of information regarding the usage (demand) of the networks, which is different from the well-known information of stops and timetables (offer). To enable analysis over these large collections of data, a compact yet indexed representation is needed that, unlike the works that focus on indexing moving objects, allows for representation and querying of relevant network elements related to passenger trips.

@@

Because smart card methods usually provide only information about boarding stops, there are works that study the challenge of inferring alighting stops from passengers \cite{wang2011review}. In addition, the authors of \cite{tao2014exploring} have specifically tackled the challenge of reconstructing full trajectories, accounting for trip-chaining, by using data obtained from smart cards. Furthermore, in \cite{alsger2016validating} it is also proven that not only the alighting stops, but also the (last) destination stop of a trip can be estimated from boarding data gathered by a smart card, within a reasonable accuracy.
